\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-05-18 paper/manuscript.tex
added new WBM downloader code + updated two figures in the manuscript

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Feb 22 21:39:50 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lr}
		\hline
		File type & Occurrences \\ 
		\hline
		.pdf & 1371 \\ 
		.html & 819 \\ 
		.png & 210 \\ 
		.jpg & 131 \\ 
		.gif &  99 \\ 
		.js &  51 \\ 
		.PDF &  50 \\ 
		.aspx &  43 \\ 
		.doc &  35 \\ 
		.css &  32 \\ 
		.JPG &  26 \\ 
		.Net &  12 \\ 
		.xlsx &   6 \\ 
		.docx &   5 \\ 
		.ttf &   3 \\ 
		.xml &   3 \\ 
		.htm &   2 \\ 
		.woff &   2 \\ 
		.xls &   2 \\ 
		.asp &   1 \\ 
		.eot &   1 \\ 
		.GIF &   1 \\ 
		.ico &   1 \\ 
		.PNG &   1 \\ 
		.ppt &   1 \\ 
		.swf &   1 \\ 
		.txt &   1 \\ 
		\hline
	\end{tabular}
	\caption{File types in scraped websites} 
\end{table}

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Feb 22 21:35:10 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lrr}
		\hline
		Website & Files & Size (MB) \\ 
		\hline
		brownsvilletn.gov & 188 & 14328 \\ 
		www.centralpointoregon.gov & 150 & 137440 \\ 
		www.dedham-ma.gov & 603 & 212572 \\ 
		www.duncanok.gov &  84 & 47064 \\ 
		www.dutchessny.gov & 110 & 291376 \\ 
		www.ennistx.gov & 200 & 26244 \\ 
		www.greenvillenc.gov & 333 & 25732 \\ 
		www.romi.gov & 491 & 112584 \\ 
		www.trumbull-ct.gov & 787 & 191540 \\ 
		www.westonct.gov & 861 & 213140 \\ 
		\hline
	\end{tabular}
	\caption{Test websites} 
\end{table}

>>>>

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Tue May 16 13:38:43 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lr}
		\hline
		Filetype & Frequency \\ 
		\hline
		& 47652 \\ 
		pdf & 9486 \\ 
		jpg & 4342 \\ 
		html & 3492 \\ 
		aspx & 2832 \\ 
		png & 2358 \\ 
		gif & 1296 \\ 
		JPG & 545 \\ 
		css & 385 \\ 
		1 & 358 \\ 
		js & 344 \\ 
		htm & 264 \\ 
		docx & 202 \\ 
		dwf & 181 \\ 
		doc & 168 \\ 
		asp & 161 \\ 
		PDF & 103 \\ 
		php &  83 \\ 
		egov &  54 \\ 
		cfm &  45 \\ 
		4 &  42 \\ 
		2 &  35 \\ 
		com &  31 \\ 
		0 &  29 \\ 
		3 &  26 \\ 
		\hline
	\end{tabular}
	\caption{The 25 most common file types in scraped websites} 
\end{table}

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Tue May 16 14:05:19 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lrr}
		\hline
		Website & Files & Size (kB) \\ 
		\hline
		attica-in.gov & 1417 & 61988 \\ 
		bedford.in.us & 560 & 57628 \\ 
		cityofboonvilleindiana.com & 110 & 9848 \\ 
		connersvillecommunity.com & 569 & 170684 \\ 
		frankfort-in.gov & 2652 & 205368 \\ 
		mitchell-in.com &  50 & 3036 \\ 
		warsaw.in.gov & 2117 & 298264 \\ 
		www.batesvilleindiana.us &   1 &  96 \\ 
		www.bernein.com & 755 & 60836 \\ 
		www.bloomington.in.gov &   1 &  52 \\ 
		www.brazil.in.gov &   1 &  36 \\ 
		www.carmel.in.gov & 8727 & 2267604 \\ 
		www.ci.auburn.in.us & 1025 & 178496 \\ 
		www.ci.bluffton.in.us &   1 & 132 \\ 
		www.cityoffortwayne.org & 4378 & 2134540 \\ 
		www.cityofhobart.org & 2463 & 718312 \\ 
		www.cityofrisingsun.com & 3311 & 991736 \\ 
		www.cityofrockport-in.gov &  98 & 11836 \\ 
		www.clintonco.com & 524 & 134344 \\ 
		www.elkhartindiana.org & 2345 & 1132612 \\ 
		www.elwoodcity-in.org &   1 &  48 \\ 
		www.evansvillegov.org & 11844 & 6339388 \\ 
		www.gary.in.us & 1227 & 371480 \\ 
		www.huntingburg-in.gov & 2496 & 388188 \\ 
		www.indy.gov & 9675 & 5717888 \\ 
		www.jasperindiana.gov & 4013 & 561212 \\ 
		www.lakestation-in.gov &   2 &  40 \\ 
		www.linton-in.gov &   1 &  32 \\ 
		www.madison-in.gov & 1848 & 528200 \\ 
		www.martinsville.in.gov & 1463 & 46544 \\ 
		www.monticelloin.gov & 753 & 33352 \\ 
		www.newhavenin.org & 626 & 84176 \\ 
		www.northvernon-in.gov & 403 & 271452 \\ 
		www.richmondindiana.gov & 1042 & 250028 \\ 
		www.southbendin.gov & 4749 & 1252624 \\ 
		www.tiptongov.com & 1151 & 130404 \\ 
		www.unioncity-in.gov &   2 &  16 \\ 
		www.winchester-in.gov & 2480 & 364368 \\ 
		\hline
	\end{tabular}
	\caption{Number of files and size of websites} 
\end{table}
